New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-07-11 paper/paper.Rmd
Some explanation of slice interactions (but slice tour not explained anywhere?)

How does it work?

Diagram of interface? Scaling

>>>>

To better explore the space we combine the manual controls for the projection with manual controls for slicing. A slice is defined by a projection, a center point that is anchoring it in the high-dimensional space and the slice thickness $h$ [@slicetour]. In the case of a single orthogonal direction on the projection plane we can pick a sequence of center points in steps along that direction to move the slice and fully cover the data space. This no longer works in higher-dimensional spaces, and we can think of picking one direction and shifting the slice along the component orthogonal to the projection plane. In practice we define the center point explicitly and calculate the slice display as explained in @slicetour. The current implementation allows the user to individually enter the components of the vector defining the center point, and updates the display by jumping to the new slice.

Potential adjustments for future work include a better visualization of the current center point, potentially with interactive graphics to move the slice similar to how the manual tour was implemented here. An alternative would be a step-wise shift of the slice towards the new center point to get a better understanding of the distribution along the selected direction.

In addition it is also useful to interactively change the slice thickness, in particular when selecting the preferred thickness $h$ (also called the slice radius) for exploring the input data. This was implemented as a slicer, and to allow the user to efficiently explore the interesting range we can provide the slider range as an input. For guidance the estimates of the number of points inside the slice as a function of the original sample size $N$ and the number of dimensions $p$ from @sectionpursuit can be used: in case of a uniform distribution inside a sphere of radius $R$ a slice with thickness $h$ will contain $N_S$ points, with 
\begin{equation}
N_S = \frac{N}{2} \left(\frac{h}{R}\right)^{p-2} \left(p - (p-2)\left(\frac{h}{R}\right)^{2}\right).
\label{eq:count}
\end{equation}

The current implementation contains a switch to change between the slice view and the projected view of the data, while keeping all other settings fixed.

### 2022-07-11 paper/paper.tex
Some explanation of slice interactions (but slice tour not explained anywhere?)

How does it work?

Diagram of interface? Scaling

>>>>

To better explore the space we combine the manual controls for the
projection with manual controls for slicing. A slice is defined by a
projection, a center point that is anchoring it in the high-dimensional
space and the slice thickness \(h\) \citep{slicetour}. In the case of a
single orthogonal direction on the projection plane we can pick a
sequence of center points in steps along that direction to move the
slice and fully cover the data space. This no longer works in
higher-dimensional spaces, and we can think of picking one direction and
shifting the slice along the component orthogonal to the projection
plane. In practice we define the center point explicitly and calculate
the slice display as explained in \citet{slicetour}. The current
implementation allows the user to individually enter the components of
the vector defining the center point, and updates the display by jumping
to the new slice.

Potential adjustments for future work include a better visualization of
the current center point, potentially with interactive graphics to move
the slice similar to how the manual tour was implemented here. An
alternative would be a step-wise shift of the slice towards the new
center point to get a better understanding of the distribution along the
selected direction.

In addition it is also useful to interactively change the slice
thickness, in particular when selecting the preferred thickness \(h\)
(also called the slice radius) for exploring the input data. This was
implemented as a slicer, and to allow the user to efficiently explore
the interesting range we can provide the slider range as an input. For
guidance the estimates of the number of points inside the slice as a
function of the original sample size \(N\) and the number of dimensions
\(p\) from \citet{sectionpursuit} can be used: in case of a uniform
distribution inside a sphere of radius \(R\) a slice with thickness
\(h\) will contain \(N_S\) points, with \begin{equation}
N_S = \frac{N}{2} \left(\frac{h}{R}\right)^{p-2} \left(p - (p-2)\left(\frac{h}{R}\right)^{2}\right).
\label{eq:count}
\end{equation}

The current implementation contains a switch to change between the slice
view and the projected view of the data, while keeping all other
settings fixed.
